Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-24 Docs/TODAES/paper.tex
modifications in algorithms listing and paper structure

%Montar os Gráficos, cores e divisões.
\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}  
\usepackage{tabularx} % in the preamble
\usepackage{graphicx} %Imagens

\usepackage{minted}
\usemintedstyle{bw}

@@

\ccsdesc[500]{Hardware~Hardware-software codesign}
\ccsdesc[500]{Hardware~Software tools for EDA}
\ccsdesc[500]{Software and its engineering~Model checking}
\ccsdesc[500]{Software and its engineering~Software verification}

@@

\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP. }

@@

\begin{bottomstuff}
A. Trindade, H. Ismail, R. Degelo, E. Galv\~ao \\
Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ \\
\and\\ \\
H. Silva and L. Cordeiro \\
Federal University of Amazonas, Brazil\\
prhsilva2012@gmail.com lucascordeiro@ufam.edu.br      \\
\end{bottomstuff}

@@

\vspace{5 mm}
In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of ESBMC and $\nu$Z tools.

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{matlab}
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{minted}
\caption{OpenMP basic Example.}
\label{lst:example}
\end{listing}

\vspace{3 mm}
In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{minted}
\caption{Example of SMT formula using $\nu$Z.}
\label{vZ}
\end{listing}

\vspace{3 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}

\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i
\end{align}

\vspace{3 mm}
\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}

%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j)
\end{align}

\vspace{3 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|EX| \leq S_0, 
\end{align}

\vspace{3 mm}
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
 Initialize Variables 
 Declare number of nodes and edges
 Declare hardware cost of each node as array (h)
 Declare software cost of each node as array (s)
 Declare communication cost of each edge (c)
 Declare the initial software cost of (S0)
 Declare transposed incidence matrix graph G (E)
 Define the solutions variable (Xi) as Boolean
 main {
  For TipH = 0 to Hmax Do {
   populate Xi with nondeterministic/test values
   Calculate s(1-x)+c|Ex| and store at variable
   Requirement isued by Assume (Variable <= S0)
   Calculate Hp cost Based on value tested of Xi
   Violation check with Assert(Hp > TipH)
  }
 }
\end{minted}
\caption{Pseudocode describing sequential ESBMC}
\label{Pseudocode-describing-ESBMC}
\end{listing}

@@

To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed. 
\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
  GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
     if(chunk.right - chunk.left > largestChunk){
           largestChunk = chunk.right - chunk.left;
           largest = chunk;
     }
   }	
   chunks.remove(largest);	
   int median = largest.left + floor((largest.right - largest.left) / 2)
   if(median > 0){
      if(largest.right - largest.left > 1)
         chunks.add(new chunk(largest.left, median - 1));	
      if(largest.right != largest.left)
         chunks.add(new chunk(median + 1, largest.right);
    }
   return median;
 }
\end{minted}
\caption{Steps calculation using intervals.}
\label{Steps-Calculation-using-Intervals}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
 step = controller.GetNextStep();
 int pid = ExecuteStep(step);
 while(isRunning(pid)){
   if(!controller.isNeeded(step))
    kill(pid);
 }
\end{minted}
\caption{Worker sample.}
\label{worker-sample}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[mathescape,
               linenos,
               numbersep=7pt,
               gobble=0,
               frame=lines,
               framesep=2mm]{c++}
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and S0
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G (E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= S0)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{minted}
\caption{Pseudocode describing ESBMC-$\nu$Z.}
\label{vZ-pseudocode}
\end{listing}

@@

@@

\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=6pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.8cm}m{0.9cm}m{0.9cm}m{8.2cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

%----------------------------------------------
\subsection{Experimental Results}
\label{Experimental-Results}
%----------------------------------------------

\begin{table*}[t]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
\\
 &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
\cmidrule(r){3-9}

>>>>

%Montar os Gráficos, cores e divisões.
\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}  
\usepackage{tabularx} % in the preamble
\usepackage{graphicx} %Imagens
\renewcommand{\lstlistingname}{Algorithm}
%\usepackage{minted}
%\usemintedstyle{bw}

@@

\ccsdesc[500]{Hardware~ Hardware-software codesign}
\ccsdesc[500]{Hardware~ Software tools for EDA}
\ccsdesc[500]{Software and its engineering~ Model checking}
\ccsdesc[500]{Software and its engineering~ Software verification}

@@

\keywords{hardware-software co-design, hardware-software partitioning, optimization, model checking, multi-core, OpenMP.}

@@

\begin{bottomstuff}
A. Trindade, H. Ismail, R. Degelo, and E. Galv\~ao \\
Graduate Program in Electrical Engineering, Federal University of Amazonas, Brazil \\
\{alessandro.b.trindade, hussamaismail, rdegelo, esj.galvao\}@gmail.com \\ 
\\
H. Silva, and L. Cordeiro \\
Federal University of Amazonas, Brazil\\
prhsilva2012@gmail.com, lucascordeiro@ufam.edu.br      \\
\end{bottomstuff}

@@

\vspace{3 mm}
In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as ESBMC and $\nu$Z can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of ESBMC and $\nu$Z tools.

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{matlab}
%int k;
%#pragma omp parallel for
%for (k = 0; k < 10; k++)
%  a[k] = 2*k;
%\end{minted}
%\caption{OpenMP basic Example.}
%\label{lst:example}
%\end{listing}

\vspace{3 mm}
\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={lst:example},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
int k;
#pragma omp parallel for
for (k = 0; k < 10; k++)
  a[k] = 2*k;
\end{lstlisting}

\vspace{1.5 mm}
In the above example, the {\it for} loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\textit{\#pragma omp critical}'' directive is routinely used.

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%              framesep=2mm]{c++}
%(Declare-Const K Int) 
%(Declare-Const W Int)
%(assert (< K 2)) 
%(assert (< (- W K) 1))
%(maximize (+ K W)) 
%(check-sat)
%\end{minted}
%\caption{Example of SMT formula using $\nu$Z.}
%\label{vZ}
%\end{listing}

\vspace{3 mm}
\begin{lstlisting}[language=C,caption={OpenMP basic Example.},label={vZ},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
(Declare-Const K Int) 
(Declare-Const W Int)
(assert (< K 2)) 
(assert (< (- W K) 1))
(maximize (+ K W)) 
(check-sat)
\end{lstlisting}

\vspace{1.5 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

@@

Based on~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $V_i \in V_h, V_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
%
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{V_i \in V_h} h_i,
\end{align}
%
\vspace{2 mm}
\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
%
%
%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{V_i \in V_s}\:s_i + \Sigma_{(V_i,V_j)\in\:E_p} c(V_i,V_j).
\end{align}

\vspace{2 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, {\it i.e.}, to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal, which is thus related to system with hard real-time constraints. Based on Eq.~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as 
%
\vspace{1 mm}
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|EX| \leq S_0, 
\end{align}

\vspace{2 mm}
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
% Initialize Variables 
% Declare number of nodes and edges
% Declare hardware cost of each node as array (h)
% Declare software cost of each node as array (s)
% Declare communication cost of each edge (c)
% Declare the initial software cost of (S0)
% Declare transposed incidence matrix graph G (E)
% Define the solutions variable (Xi) as Boolean
% main {
%  For TipH = 0 to Hmax Do {
%   populate Xi with nondeterministic/test values
%   Calculate s(1-x)+c|Ex| and store at variable
%   Requirement isued by Assume (Variable <= S0)
%   Calculate Hp cost Based on value tested of Xi
%   Violation check with Assert(Hp > TipH)
%  }
% }
%\end{minted}
%\caption{Pseudocode describing sequential ESBMC}
%\label{Pseudocode-describing-ESBMC}
%\end{listing}

\vspace{1.5 mm}
\begin{lstlisting}[caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial software cost of ($S_0$)
Declare transposed incidence matrix graph G (E)
Define the solutions variable ($X_i$) as Boolean
main {
  For TipH = 0 to Hmax Do {
    Populate $X_i$ with nondeterministic / test values
    Calculate s(1-x)+c|Ex| and store at variable
    Requirement isued by Assume (Variable <= $S_0$)
    Calculate Hp cost Based on value tested of $X_i$
    Violation check with Assert(Hp > TipH)
  }
}
\end{lstlisting}

@@

To optimize the CPU resources utilization without modifying the underlying SMT solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ESBMC sequential-search ``ESBMC-SS''.
\begin{figure}[h]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[h]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS approach.}
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

Algorithm~\ref{Steps-Calculation-using-Intervals} describes how the customized binary search calculates and returns the step to be executed.

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right-largest.left)/2)
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
% step = controller.GetNextStep();
% int pid = ExecuteStep(step);
% while(isRunning(pid)){
%   if(!controller.isNeeded(step))
%    kill(pid);
% }
%\end{minted}
%\caption{Worker sample.}
%\label{worker-sample}
%\end{listing}

\vspace {2 mm}
\begin{lstlisting}[caption={Worker sample.},label={worker-sample},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
step = controller.GetNextStep();
int pid = ExecuteStep(step);
while(isRunning(pid)){
  if(!controller.isNeeded(step))
    kill(pid);
}
\end{lstlisting}

@@

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%--Initialize Variables
%  Create vZ context 
%  Create binary vector (x)
%  Declare number of nodes, edges and S0
%  Declare hardware cost of each node as array (h) 
%  Declare software cost of each node as array (s)
%  Declare communication cost of each edge (c)
%  Declare transposed incidence matrix graph G (E)
%--Arithmetic Expressions
%  SC = s(1-x)
%  CMC = c*|EX|
%  Fobj =  x[i] * h[i]
%--Assert Constraints
%  Add constraints (SF + CMC <= S0)
%  Add constraints to minimize Fobj
%  Check Model
%  Print Result
%\end{minted}
%\caption{Pseudocode describing ESBMC-$\nu$Z.}
%\label{vZ-pseudocode}
%\end{listing}

\vspace {2 mm}
\begin{lstlisting}[caption={Pseudocode describing ESBMC-$\nu$Z.},label={vZ-pseudocode},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny,mathescape=true]
--Initialize Variables
  Create vZ context 
  Create binary vector (x)
  Declare number of nodes, edges and $S_0$
  Declare hardware cost of each node as array (h) 
  Declare software cost of each node as array (s)
  Declare communication cost of each edge (c)
  Declare transposed incidence matrix graph G(E)
--Arithmetic Expressions
  SC = s(1-x)
  CMC = c*|EX|
  Fobj =  x[i] * h[i]
--Assert Constraints
  Add constraints (SF + CMC <= $S_0$)
  Add constraints to minimize Fobj
  Check Model
  Print Result
\end{lstlisting}

@@

\vspace{1.5 mm}
\begin{minipage}{\linewidth}
\centering
\small
\sffamily\small
\tabulinesep=4pt
\captionof{table}{Description of Benchmarks.} 
\begin{tabular}[c]{m{1.5cm}m{0.7cm}m{0.7cm}m{8.9cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree \cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\label{tab:Description-of-Benchmarks} 
\end{tabular}\par
\bigskip
\end{minipage}

@@

@@

%----------------------------------------------
\subsection{Experimental Results}
\label{Experimental-Results}
%----------------------------------------------
%
\begin{table*}[h]
  \centering
  \caption{Experimental results of the HW-SW partitioning benchmarks.}  
  \begin{tabular}{*{9}{cc|c|c|c|c|c|c|c}}
\\
 &  & \rotatebox{90}{\textbf{\normalsize{CRC32}}} & \rotatebox{90}{\textbf{\normalsize{Patricia}}} & \rotatebox{90}{\textbf{\normalsize{Dijkstra}}} & \rotatebox{90}{\textbf{\normalsize{Clustering}}} & \rotatebox{90}{\textbf{\normalsize{RC6}}} & \rotatebox{90}{\textbf{\normalsize{Fuzzy}}} & \rotatebox{90}{\textbf{\normalsize{Mars}}} \\[0.15cm]
\cmidrule(r){3-9}
